---
title: "Joins"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{joins}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(colortable)
library(knitr)
```

## Joins

A common practice in data science is to be handed two datasets with some set or variables that act as a key between them.
The way to combine these two datasets since they likely contain useful information required is through the use of a `join`. 

{dplyr} luckily comes with several joins that can help you take care of these combinations. 
However, each of the types of joins can have unintended side effects that you don't expect.

For example, an full join will keep ID's from both data.frames!

```{r multi-join}

# From dplyr::join documentation
band_members %>% full_join(band_instruments)

```

In this toy example, we can clearly see that we ended up with 4 rows, not the three you might have expected.

## Colortable to the rescue!

With colortable, we can color the one of the output fields that we expect to remain unique and easily see if something is not as we expect.

After the merge, we can see that keith is new!

```{r color-join}

band_members$name <- color_vctr(band_members$name,text_color = "blue")

band_members %>% full_join(band_instruments, on = "name")

```

### Additional Joins




